
---
title: "Cross Validation Strategies"
author: "Deniz Akdemir"
date: "Date"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(ggplot2)
load("plots.RData")
```

### 2. **Leave 20% of the Wheat Lines Out for Validation (Strategy 1)**

This section includes the plots where 20% of the wheat lines are left out for validation. The plots `p1_12`, `p1_17`, `p1_12_int`, and `p1_17_int` represent different sub-strategies or data configurations.

#### Without Interaction Term

```{r, fig.cap="Results without interaction term using dataset 12 "}
plot(p1_12)
```

```{r, fig.cap="Results without interaction term using dataset 17"}
plot(p1_17)
```

#### With Interaction Term

```{r, fig.cap="Results with interaction term using dataset 12"}
plot(p1_int_12)
```

```{r, fig.cap="Results with interaction term using dataset  17"}
plot(p1_int_17)
```

### 3. **Leave One Mix Out for Validation (Strategy 2)**

In this section, one entire mix is left out for validation purposes. Here, you will display `p2_12`, `p2_17`, `p2_12_int`, and `p2_17_int`.

#### Without Interaction Term

```{r, fig.cap="Results without interaction term using dataset 12  in Strategy 2"}
plot(p2_12)
```

```{r, fig.cap="Results without interaction term using dataset 17 in Strategy 2"}
plot(p2_17)
```

#### With Interaction Term

```{r, fig.cap="Results with interaction term using dataset 12 in Strategy 2"}
plot(p2_12_int)
```

```{r, fig.cap="Results with interaction term using dataset  17 in Strategy 2"}
plot(p2_17_int)
```

### 4. **Combined Strategy: Leave One Mix and 20% of Wheat Lines Out (Strategy 3)**

This section covers the scenario where one mix and 20% of the wheat lines are simultaneously left out for validation. Plots `p3_12`, `p3_17`, `p3_12_int`, and `p3_17_int` should be displayed here.

#### Without Interaction Term

```{r, fig.cap="Results without interaction term using dataset 12  in Strategy 3"}
plot(p3_12)
```


```{r, fig.cap="Results without interaction term using dataset  17 in Strategy 3"}
plot(p3_17)
```
#### With Interaction Term

```{r, fig.cap="Results with interaction term using dataset 12  in Strategy 3"}
plot(p3_12_int)
```

```{r, fig.cap="Results with interaction term using dataset  17 in Strategy 3"}
plot(p3_17_int)
```


#### Outputs in table form




```{r load-data, echo=FALSE, message=FALSE}
load("meanCors.RData")
library(knitr)
library(DT) # Optional, for interactive tables
```




## Scenario 1: Leave 20% of Wheat Lines Out

### Dataset 12

```{r, echo=FALSE}
kable(means_long_12)
```

### Dataset 17

```{r, echo=FALSE}
kable(means_long_17)
```

### Dataset 12 with Interaction Term

```{r, echo=FALSE}
kable(means_long_12_int)
```

### Dataset 17 with Interaction Term

```{r, echo=FALSE}
kable(means_long_17_int)
```

#### Scenario 2: Leave One Mix Out for Validation

```markdown
## Scenario 2: Leave One Mix Out

### Dataset 12

```{r, echo=FALSE}
kable(means_long_12_scenario2)
```

### Dataset 17

```{r, echo=FALSE}
kable(means_long_17_scenario2)
```

### Dataset 12 with Interaction Term

```{r, echo=FALSE}
kable(means_long_12_int_scenario2)
```

### Dataset 17 with Interaction Term

```{r, echo=FALSE}
kable(means_long_17_int_scenario2)
```


### 5. **Conclusion**
